%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{deedy-resume}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\rfoot{Page \thepage \hspace{1pt}}
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Elizabeth P. Wu}{}{
\href{mailto:ewu12@jhu.edu}{ewu12@jhu.edu} | 415.377.9757
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.3\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{Johns Hopkins University}
\descript{Biomedical Engineering}
\location{Conc. in Biomechanics}
\location{B.S. expected May 2020}
GPA: 3.69
\sectionsep

\subsection{Lick-Wilmerding High School}
\location{May 2016|  San Francisco, CA}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Awards
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Awards}
Dean's List (2016-present)\\
National Merit Finalist\\
Nelson F. Peterson Scholarship\\
FIRST Tech Challenge Robotics NorCal Finalist\\
Team USA, Triathlon Age Group
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
\underline{Personal Projects}\\
Instagram: \href{https://www.instagram.com/elizabethwu12/}{\bf elizabethwu12} \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
Organic Chemistry 1+2\\
Manufacturing Engineering\\
Systems and Controls\\
Molecules and Cells\\
Models and Simulations\\
Mastering Electronics\\
Systems Bioengineering (Data Science)\\
Biomaterials\\


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Manufacturing}
\location{Proficient:}
Solidworks \textbullet{}   3D printing \textbullet{} Laser cutting \\
\location{Familiar:}
Wire EDM \textbullet{} Lathe \textbullet{} Mill \textbullet{} Casting \\
\sectionsep
\subsection{Programming}
\location{Intermediate:}
C \textbullet{} C++ \textbullet{} Java \textbullet{} Matlab \textbullet \LaTeX \\
\location{Familiar:}
Python
\sectionsep
\subsection{Language}
English \textbullet{} Chinese (Mandarin)
\sectionsep
\subsection{Misc}
Basic graphic design \textbullet{} Adobe Suite\\
Video editing \textbullet{} Writing\\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{UCSF Surgical Innovations} \\
\descript{Roy Lab and Harrison Lab | Engineering Intern}
\location{May 2019 -- August 2019 | San Francisco, CA}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Prototyped soft pneumatic actuators for SmartDerm, a device to prevent pressure ulcers
\item Performed data analysis on patient data for 
\end{tightemize}
\sectionsep

\runsubsection{Johns Hopkins University Applied Physics Laboratory} \\
\descript{Research and Exploratory Development | Technical Assistant}
\location{May 2018 -- August 2018 | Laurel, MD}
%\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Performed testing of overpressure wave effects on human head and neck to improve the safety of personal protective equipment for warfighters.
\item Performed testing and analysis of a novel head surrogate that provides quantitative, temporal, and biofidelic data for ballistic testing of warfighter helmets.
\item Documented both projects as a deliverable to the government sponsor.
\item Adjusted CAD files for 3D print and CNC lathing of test equipment.
\item Showed initiative and self-motivation by finding projects to work on.
\item Wrote 5 standard operating procedures for internal use.
\end{tightemize}
\sectionsep

\runsubsection{Whiting School of Engineering Manufacturing}
\descript{| Makerspace Teaching Assistant}
\location{August 2017 -- Present | Baltimore, MD}
%\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Writes documentation on tools for use by Hopkins students and affiliates.
\item Works on projects, such as making a virtual reality tour and designing demonstration parts.
\item Maintains equipment and assists students with FDM printing, laser cutting, and woodwork.
\end{tightemize}
\sectionsep

\runsubsection{Kaleyedos}
\descript{| Co-founder and Lead Prototype Developer}
\location{December 2016 -- 2017 | Baltimore, MD}
\begin{tightemize}
\item Core member of CBID design team creating an inexpensive, deskilled, cloud-integrated tool that uses computer vision concepts to aid in diagnosis of Retinopathy of Prematurity in a NICU setting.
\item Designed a universal phone fundoscope and standalone device for laboratory testing and demonstrations at competition.
\item Created visuals and diagrams for research papers, scientific posters, and patent applications.
\item Represented Kaleyedos at 5 business competitions (Kaleyedos was recognized in 12 national competitions, winning \$50,000 total).
\end{tightemize}
\sectionsep

\runsubsection{Digital Media Center}
\descript{| Special Projects}
\location{October 2016 -- 2018 | Baltimore, MD}
\begin{tightemize}
\item Designed hacker workshops and maintained 3D printers.
\item Consulted for patron projects and taught skills necessary for implementation.
\item Expected to have good interpersonal communication skills and teamwork ability.
%\item Greeted patrons and maintained inventory of camera and audio equipment.
\end{tightemize}
\sectionsep

\runsubsection{TacPac}
\descript{| Lead Prototype Developer}
\location{September 2017 -- December 2017 | Baltimore, MD}
\begin{tightemize}
\item Prototyped device to reduce organ transplant rejections by creating an automated immunoassay system with a telemedicine pipeline to accurately gauge Tacrolimus levels in the blood.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Class Projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\runsubsection{Predictive Approach to Acute Kidney Injury} \\
\descript{ | Data Analyist}
\location{May 2019 -- August 2019 | San Francisco, CA}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Prototyped soft pneumatic actuators for SmartDerm, a device to prevent pressure ulcers
\item Performed analysis on patient data for Tabla, a device to aid in diagnosis of lung disease using percussion (manuscript pending)
\item Manufactured silicone wafer artificial lung using CNC mill and SLA printer for animal studies
\item 
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Extracirriculars
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Extracirriculars}
\runsubsection{Residential Advisor}
\descript{}
\location{August 2018 -- December 2018 | Baltimore, MD}
\begin{tightemize}
\item Supervises 46 residents, organizes weekly floor programs, and assists residents with personal and academic issues.
\item Responsible for student safety and policy enforcement on weekly duty nights.
\end{tightemize}
\sectionsep

\end{minipage} 
\end{document}  \documentclass[]{article}
